\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Work on the conclusion

The task was performance-oriented and yet we were interested in accessing and
understanding the cognitive mechanisms at stake during the interaction: where do
the participant look when they want to understand a robot behaviour? does
\emph{anticipation} reflect understanding? how the robot's design impact the
interaction?

@@

One need to be aware of its limitations: eye-tracking does not give a direct
access to underlying mental representations, and a gaze pattern does not
automatically tell us what the subject think of (EEG or fMRI may be slightly
closer to that target, but they come with their own range of limitations).

@@

The results show that the way the sensor data is visualised has an
impact on both the gaze patterns and the performance (Question 2).
However, for the relation between the gaze patterns of the participants
and their performance outcomes (Question 1) we cannot claim a direct
relation. We found a negative correlation between the gaze-patterns and
the first improvement during the interaction phase. We could not find a
relation between the explanation of the participants and their
gaze-patterns. Moreover, we did not find any anticipation patterns in
the gaze data. The lack of evidence for the relation between
participants' explanations and their gaze patterns prevents us to make
any strong claims about the relation between the overall performance and
the gaze patterns.

%
%The fact that we cannot find a relation between the gaze patterns and
%all the factors in the performance might have its roots in the way we
%designed the interaction phase experiment. As a working hypothesis we
%said that there should be clear and carefully designed mapping between
%the robots' behaviour and the sensor data visualization. Its environment
%also affects the behaviour of the robot and hence the environment also
%should be taken into consideration while designing the
%behavior-visualisation mapping. We introduced a novelty (the gray
%obstacle being more reflective) in the environment during the
%interaction phase of the experiment that forced the participants to
%revise their hypothesis and hence they failed to understand the robot's
%functionality. This also serves as a word of caution in future while
%designing such interactions. The observation phase serves as a training
%session for the participants, which can later be tested during the
%interaction phase. Any novel behaviour modality (in our case, the more
%reflective grey obstacle) can have a negative impact on the
%participants' understanding.

In a nutshell, the use of gaze data as an assessment of the human-robot
interaction in an educational setting provides future research
prospects. The data acquisition is a better trade-off between the
ecological validity of the experiment (as there cannot be an interaction
with the robot fMRI data acquisition) and the precision of the data
stream (wristbands for measuring the palpitation and the temperature).

>>>>

The task was performance-oriented and yet we were interested in accessing and
understanding the cognitive mechanisms at stake during the interaction: where do
the participant look when they want to understand a robot behaviour? Does
\emph{anticipation} reflect understanding? How the robot's design impact the
interaction?

@@

In that regard, we identify three main strengths of eye-tracking. First,
eye-tracking introduce less experimental bias: mobile eye-tracker are
non-invasive and lightweight. Combined with mobile recording units, they do not
put any constraints on participant movements, contrary to traditional techniques
like video recording. Also, contrary to questionnaires or interview-based
protocol where the experimenter active role may influence the assessment,
eye-tracker are easy to ``forget about'' for the participants.

Second, eye-tracking provides a direct, un-mediated access to the subject's
attentional focus~\cite{sharma2014withmeness} (both spatially -- where does the
subject look at -- and temporally -- where does the subject's attention stays).
Importantly, this information leads to a fine-grained measure of
\emph{engagement}.  Also, the good temporal resolution of eye-trackers allows
for the accurate study of the \emph{dynamics} of attention: what are the
attentional patterns of the subject during the interaction.

Third, it has been showed in literature that eye-tracking can provide an
effective measure of higher socio-cognitive behaviours: it can be used as a
predictor for successful joint task achievement~\cite{sharma2013understanding},
or as a measure of \emph{interaction quality}~\cite{jermann2012effects} through
measurement of joint attention.

One need however to be aware of its limitations: eye-tracking does not give a direct
access to underlying mental representations, and a gaze pattern does not
automatically tell us what the subject think of (EEG or fMRI may be slightly
closer to that target, but they come with their own range of limitations).

@@

Still, we believe that eye-tracking, as a method for the assessment and
understanding of the complex cognitive mechanisms that underlie human-robot
interaction, is a promising tool, currently under-used in robotics.

%In a nutshell, the use of gaze data as an assessment of the human-robot
%interaction in an educational setting provides future research
%prospects. The data acquisition is a better trade-off between the
%ecological validity of the experiment (as there cannot be an interaction
%with the robot fMRI data acquisition) and the precision of the data
%stream (wristbands for measuring the palpitation and the temperature).
